reOpt Data

### 2023-01-22 src/climate_risk.Rmd
sensitivity analysis data (mean, 95th percentile and distribution) in reopt.Rmd and climate_risk.Rmd

library(tidyverse)
library(janitor)
library(googlesheets4)
```

@@

>>>>

library(tidyverse)
library(janitor)
library(googlesheets4)
library(ggplot2)
```

@@

```{r}
#mean ("mean_metric"), 95th percentile ("perc_metric"), and distribution for sensitivity analysis

mean_climate_risk <- mean(climate_risk_cbsa_stcofips$normalized_inverted_climate_risk)
mean_climate_risk

perc_climate_risk <- quantile(climate_risk_cbsa_stcofips$normalized_inverted_climate_risk, probs = 0.95)
perc_climate_risk

climate_risk_distribution <- density(climate_risk_cbsa_stcofips$normalized_inverted_climate_risk)
plot(climate_risk_distribution)
```

### 2023-01-22 src/reopt.Rmd
output normalized metrics to google sheets
sensitivity analysis data (mean, 95th percentile and distribution) in reopt.Rmd and climate_risk.Rmd

>>>>

```{r}
sheet_write(reopt_metrics_normalized, ss = "https://docs.google.com/spreadsheets/d/1VROhOTWY4jSeI_zNgFui4ie6QiIz7uzzli8rF72fAyg/edit#gid=498103540", sheet = "normalized_reopt_metrics")
```

```{r}
# mean ("mean_metric"), 95th percentile ("perc_metric"), and distribution for sensitivity analysis

#energy production 
mean_energy_production <- mean(energy_production_metric$normalized_annual_renewable)
mean_energy_production

perc_energy_production <- quantile(energy_production_metric$normalized_annual_renewable, probs = 0.95)
perc_energy_production

energy_distribution <- density(energy_production_metric$normalized_annual_renewable)
plot(energy_distribution)

#climate impacts
mean_total_co2 <- mean(climate_impacts_metric$inverted_n_total_co2)
mean_total_co2

perc_total_co2 <- quantile(climate_impacts_metric$inverted_n_total_co2, probs = 0.95)
perc_total_co2

climate_impacts_distribution <- density(climate_impacts_metric$inverted_n_total_co2)
plot(climate_impacts_distribution)

#financial
mean_irr <- mean(financial_metric$normalized_irr)
mean_irr

perc_irr <- quantile(financial_metric$normalized_irr, probs = 0.95)
perc_irr

irr_distribution <- density(financial_metric$normalized_irr)
plot(irr_distribution)

#health impacts
mean_health_emissions <- mean(health_impact_metric$inverted_n_health_emissions_cost)
mean_health_emissions

perc_health <- quantile(health_impact_metric$inverted_n_health_emissions_cost, probs = 0.95)
perc_health

health_distribution <- density(health_impact_metric$inverted_n_health_emissions_cost)
plot(health_distribution)
```
